% Source code for my CV
%
% https://www.kent.ac.uk/careers/cv/msccompcv.htm
% https://math.berkeley.edu/~williams/CV.pdf

\documentclass[10pt,a4paper]{moderncv}
\usepackage[utf8]{inputenc}
% List of themes: http://tex.stackexchange.com/a/44222/89290
\moderncvtheme[black]{banking}

\firstname{Matt}
\familyname{Gaikema}
\address{22619 Arbor Stream Dr}{77450 Katy, Tx}
\mobile{(832)-683-9857}
\email{mgaikema1@gmail.com}
\homepage{www.mattgaikema.com}
\social[github]{TexAgg}
\social[linkedin]{matthew-gaikema}

\begin{document}
\makecvtitle

%%%%%%%%%%%%%
% EDUCATION %
%%%%%%%%%%%%%

\section{Education}

\cventry{2014 - 2018}{Bachelor of Science in \textbf{Computer Science} and \textbf{Applied Mathematics}}
{Texas A\&M University}
{College Station, Texas}
{3.75/4.0}
{University Honors Fellow}
\cvitem{Courses}{
    \begin{itemize}
        \item Stat 211\&212: Principles of Statistics I\&II
        \item CSCE 221: Data Structures and Algorithms
        \item Math 308: Differential Equations
        \item Math 323: Linear Algebra
        \item CSCE 312: Computer Organization
        \item CSCE 314: Programming Languages
        \item Math 409: Advanced Calculus
        \item Math 411: Math Probability
        \item Math 415\&416: Modern Algebra I\&II
        \item Math 407: Complex Variables
        \item Math 414: Fourier Series and Wavelets
        \item Math 442: Math Modeling
        \item Math 470: Cryptography
    \end{itemize}
}


%%%%%%%%%%
% SKILLS %
%%%%%%%%%%

\section{Computer Skills}
\cvitem{Languages}{C++, Mathematica, \LaTeX, Java, R, Javascript, PHP, C\#, Python}
\cvitem{Software}{NodeJS, CMake, Git, Linux, ASP.NET MVC, Flask}
%\cvline{Passed Actuarial Exam P}{Scored 6/10}


%%%%%%%%%%%%%%%%%%%%%%%
% RESEARCH EXPERIENCE %
%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Experience}

\cventry{Fall 2016 - Present}{Undergraduate Research Assistant}{Department of Computer Science}{Texas A\&M University}{}{
    \begin{itemize}
        \item Research parametrized algorithms for hard problems.
    \end{itemize}
}
\cventry{Summer 2016}{Undergraduate Research Assistant}{Department of Mathematics}{Texas A\&M University}{}{
    \begin{itemize}
        \item Discovered formula determining the total number of different transposition decompositions of a permutation cycle.
        \item Developed a program to compute the entries and eigensystem of the integer partition matrix.
    \end{itemize}
}
\cventry{Summer 2015}{Undergraduate Research Assistant}{Department of Mathematics}{Texas A\&M University}{}{
    \begin{itemize}
        \item Analyzed sound quality of vinyls from before and after RIAA standardization to improve sound quality in old recordings.
    \end{itemize}
}


%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE %
%%%%%%%%%%%%%%%%%%%

\section{Work Experience}

\cventry{2016 - Present}{Peer Teacher}{Department of Computer Science}{Texas A\&M University}{}{
    \begin{itemize}
        \item Support six professors in their course load by mentoring and tutoring hundreds of students in computer science.
        \item Assist students one-on-one with debugging and analyzing their C++ programs in office hours.
        \item Selected to lead weekly review lessons on discrete mathematics.
    \end{itemize}
}
\cventry{2015 - Present}{Student Assistant}{Department of Mathematics}{Texas A\&M University}{}
{
    \begin{itemize}
        \item Graded homework and exams for multivariate calculus class of over 90 students.
    \end{itemize}
}
\cventry{Summer 2016}{SMaRT Camp Counselor}{Department of Mathematics}{Texas A\&M University}{}{
    \begin{itemize}
        \item Served as a counselor at a two-week math camp for twenty gifted high school students from around the country.
        \item Taught students how to make formal proofs and introduced them to advanced mathematics topics.
    \end{itemize}
}


%%%%%%%%%%%%%%
% LEADERSHIP %
%%%%%%%%%%%%%%

\section{Leadership}

\cventry{2016 - Present}{Webmaster}{Math Club}{}{}{
    \begin{itemize}
        \item Created website for Math Club (main department student organization) from scratch, using PHP.
        \item Maintain and update website, and communicate upcoming events.
    \end{itemize}
}
\cventry{2016 - Present}{Web Developer}{Aggie Coding Club}{}{}{
    \begin{itemize}
        \item Key member of the development team for the original website.
    \end{itemize}
}
\cventry{Summer 2014}{Participant}{Champe-Fitzhugh International Honors Leadership Seminar}{}{}{
    \begin{itemize}
        \item Selected as part of a competitive process to be one of 30 incoming Texas A\&M student participants.
        \item Traveled throughout Italy and attended lectures and tours on Italian art, architecture, and culture.
    \end{itemize}
}



%%%%%%%%%%
% HONORS %
%%%%%%%%%%

\section{Honors and Awards}

\cvline{Pi Mu Epsilon (Math Honor Society)}{(2015-2016)---Elected Webmaster}
\cvline{National Merit Scholar}{(2014 - 2018)}
\cvline{Texas A\&M President's Endowed Scholar}{(2014 - 2018)}
\cvline{HackDFW}{(2016) Won Ilumi SmartBulb prize by developing Android app which provided light therapy for different medical conditions by automatically controlling light color and intensity.}
\cvline{Capital One Summit for Developing  Leaders}{(2015)}


%%%%%%%%%%%%%%%
% CONFERENCES %
%%%%%%%%%%%%%%%

\section{Conferences}

\cvline{Math Fest}{(2015) One of two students selected by honors faculty to attend national math conference.}

\end{document}