\documentclass[10pt,a4paper]{moderncv}
\usepackage[utf8]{inputenc}
% http://tex.stackexchange.com/a/39030/89290
% http://tex.stackexchange.com/a/68797/89290
\usepackage[scale=0.75, top=1.5cm, left=1.5cm, right=1.5cm, bottom=1.5cm, bmargin=1cm, footnotesep=1cm]{geometry}
\moderncvtheme[black]{banking}
% http://tex.stackexchange.com/a/191768/89290
\nopagenumbers

\firstname{Matt}
\familyname{Gaikema}
\address{22619 Arbor Stream Dr}{77450 Katy, Tx}
\mobile{(832)-683-9857}
\email{mgaikema1@gmail.com}
\homepage{www.mattgaikema.com}
\social[github]{TexAgg}

\begin{document}
\vspace*{-2\baselineskip}
\makecvtitle
\vspace*{-2\baselineskip}


%%%%%%%%%%%%%
% OBJECTIVE %
%%%%%%%%%%%%%

\section{Objective}

To obtain a Summer 2017 Internship in Computer Science.

\vspace*{-1\baselineskip}


%%%%%%%%%%%%%
% EDUCATION %
%%%%%%%%%%%%%

\section{Education}

\cventry{2014 - 2018}{Bachelor of Science in \textbf{Computer Science} and \textbf{Applied Mathematics}}
{Texas A\&M University}
{College Station, Texas}
{3.75/4.0}
{University Honors Fellow}

\vspace*{-1\baselineskip}


%%%%%%%%%%
% SKILLS %
%%%%%%%%%%

\section{Skills}
% http://tex.stackexchange.com/questions/95045/how-to-prevent-breaklines-inside-cvcomputer-in-moderncv
\cvitem{Languages}{C++, Java, R, Mathematica, Javascript, PHP, C\#, Python, \LaTeX}
\cvitem{Software}{NodeJS, CMake, Git, Linux, ASP.NET MVC, Flask}

\vspace*{-1\baselineskip}


%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE %
%%%%%%%%%%%%%%%%%%%

\section{Work Experience}

\cventry{2016 - Present}{Peer Teacher}{Department of Computer Science}{Texas A\&M University}{}{
    \begin{itemize}
        \item Support six professors in their course load by mentoring and tutoring hundreds of students in computer science.
        \item Assist students one-on-one with debugging and analyzing their C++ programs in office hours.
        \item Selected to lead weekly review lessons on discrete mathematics.
    \end{itemize}
}
\cventry{2015 - Present}{Research Assistant}{Department of Mathematics}{Texas A\&M University}{}{
    \begin{itemize}
        \item Analyzed sound quality of vinyls from before and after RIAA standardization to improve sound quality in old recordings (2015).
        \item Discovered formula determining the total number of different transposition decompositions of a permutation cycle (2016).
        \item Developed a program to compute the entries and eigensystem of the integer partition matrix.
    \end{itemize}
}
\cventry{2015 - Present}{Student Assistant}{Department of Mathematics}{Texas A\&M University}{}
{
    \begin{itemize}
        \item Graded homework and exams for multivariate calculus class of over 90 students.
    \end{itemize}
}
\cventry{Summer 2016}{SMaRT Camp Counselor}{Department of Mathematics}{Texas A\&M University}{}{
    \begin{itemize}
        \item Served as a counselor at a two-week math camp for twenty gifted high school students from around the country.
        \item Taught students how to make formal proofs and introduced them to advanced mathematics topics.
    \end{itemize}
}

\vspace*{-1\baselineskip}


%%%%%%%%%%%%%%
% LEADERSHIP %
%%%%%%%%%%%%%%

\section{Leadership}

\cventry{2016 - Present}{Webmaster}{Math Club}{}{}{
    \begin{itemize}
        \item Created website for Math Club (main department student group) from scratch, using PHP.
        \item Maintain and update website, and communicate upcoming events.
    \end{itemize}
}
\cventry{2016 - Present}{Web Developer}{Aggie Coding Club}{}{}{
    \begin{itemize}
        \item Key member of the development team for the original website.
        \item Created the information page.
    \end{itemize}
}
\cventry{Summer 2014}{Participant}{Champe-Fitzhugh International Honors Leadership Seminar}{}{}{
    \begin{itemize}
        \item Selected as part of a competitive process to be one of 30 incoming Texas A\&M student participants.
        \item Traveled throughout Italy and attended lectures and tours on Italian art, architecture, and culture.
    \end{itemize}
}

\vspace*{-1\baselineskip}


%%%%%%%%%%
% HONORS %
%%%%%%%%%%

\section{Honors and Awards}

\vspace*{-1\baselineskip}
\cventry{2016}{First place in HackDFW Ilumi Smart Bulb challenge}{}{}{}{}
\vspace*{-1.5\baselineskip}
% National Merit Scholar
\cventry{}{National Merit Scholar}{}{}{}{}
\vspace*{-1.5\baselineskip}
% PES
\cventry{}{President's Endowed Scholarship}{}{}{}{}
\vspace*{-1.5\baselineskip}
% PME
\cventry{2015 - 2016}{Member of Pi Mu Epsilon (Math Honor Society)}{}{}{}{
Elected Webmaster (2016)}
\vspace*{-1\baselineskip}
% Honors student
\cventry{}{Honors in Mathematics and Engineering}{}{}{}{}
\vspace*{-1.5\baselineskip}
\cventry{2015}{MathFest}{}{}{}{
    \begin{itemize}
        \item One of two students selected by Math Honors faculty to attend national math conference, with all expenses paid.
    \end{itemize}
}

\end{document}