% Source code for my resume.

\documentclass[10pt,a4paper]{moderncv}
\usepackage[utf8]{inputenc}
% http://tex.stackexchange.com/a/39030/89290
% http://tex.stackexchange.com/a/68797/89290
\usepackage[scale=0.75, top=2cm, left=2cm, right=2cm, bottom=2cm, bmargin=1cm, footnotesep=1cm]{geometry}
\moderncvtheme[black]{banking}
% http://tex.stackexchange.com/a/191768/89290
\nopagenumbers

\firstname{Matt}
\familyname{Gaikema}
\address{22619 Arbor Stream Dr}{77450 Katy, Tx}
\mobile{(832)-683-9857}
\email{mgaikema1@gmail.com}
\homepage{www.mattgaikema.com}
\social[github]{TexAgg}
%\social[linkedin]{matthew-gaikema}

\begin{document}
\vspace*{-2\baselineskip}
\makecvtitle
\vspace*{-2\baselineskip}


%%%%%%%%%%%%%
% OBJECTIVE %
%%%%%%%%%%%%%

\section{Objective}

To obtain a Summer 2017 Internship in Software Engineering.

\vspace*{-1\baselineskip}


%%%%%%%%%%%%%
% EDUCATION %
%%%%%%%%%%%%%

\section{Education}

\cventry{2014 - 2018}{Bachelor of Science in \textbf{Computer Science} and \textbf{Applied Mathematics}}
{Texas A\&M University}
{College Station, Texas}
{3.75/4.0}
{University Honors Fellow}

\vspace*{-1\baselineskip}


%%%%%%%%%%
% SKILLS %
%%%%%%%%%%

\section{Skills}
% http://tex.stackexchange.com/questions/95045/how-to-prevent-breaklines-inside-cvcomputer-in-moderncv
\cvitem{Languages}{
\BLOCK{ for language in languages }
    \VAR{language},
\BLOCK{ endfor }
}
\cvitem{Software}{
\BLOCK{ for s in software }
    \VAR{s},
\BLOCK{ endfor }
}
\cvline{Passed Actuarial Exam P}{Scored 6/10}

\vspace*{-1\baselineskip}


%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE %
%%%%%%%%%%%%%%%%%%%

\section{Work Experience}

\cventry{2016 - Present}{Peer Teacher}{Department of Computer Science}{Texas A\&M University}{}{
    \begin{itemize}
        \item Support six professors in their course load by mentoring and tutoring hundreds of students in computer science.
        \item Assist students one-on-one with debugging and analyzing their C++ programs in office hours.
        \item Selected to lead weekly review lessons on discrete mathematics.
    \end{itemize}
}
\cventry{2016 - Present}{Research Assistant}{Department of Computer Science}{Texas A\&M University}{}{
    \begin{itemize}
        \item Research parametrized algorithms for hard problems.
    \end{itemize}
}
\cventry{2015 - Present}{Research Assistant}{Department of Mathematics}{Texas A\&M University}{}{
    \begin{itemize}
        \item Analyzed sound quality of vinyls from before and after RIAA standardization to improve sound quality in old recordings (2015).
        \item Discovered formula determining the total number of different transposition decompositions of a permutation cycle (2016).
        \item Developed a program to compute the entries and eigensystem of the integer partition matrix.
    \end{itemize}
}
\cventry{2015 - Present}{Student Assistant}{Department of Mathematics}{Texas A\&M University}{}
{
    \begin{itemize}
        \item Graded homework and exams for multivariate calculus class of over 90 students.
    \end{itemize}
}
\cventry{Summer 2016}{SMaRT Camp Counselor}{Department of Mathematics}{Texas A\&M University}{}{
    \begin{itemize}
        \item Served as a counselor at a two-week math camp for twenty gifted high school students from around the country.
        \item Taught students how to make formal proofs and introduced them to advanced mathematics topics.
    \end{itemize}
}

\vspace*{-1\baselineskip}


%%%%%%%%%%%%%%
% LEADERSHIP %
%%%%%%%%%%%%%%

\section{Leadership}

\cventry{2016 - Present}{Webmaster}{Math Club}{}{}{
    \begin{itemize}
        \item Created website for Math Club (main department student group) from scratch, using PHP.
        \item Maintain and update website, and communicate upcoming events.
    \end{itemize}
}
\cventry{2016 - Present}{Web Developer}{Aggie Coding Club}{}{}{
    \begin{itemize}
        \item Key member of the development team for the original website.
    \end{itemize}
}
\cventry{Summer 2014}{Participant}{Champe-Fitzhugh International Honors Leadership Seminar}{}{}{
    \begin{itemize}
        \item Selected as part of a competitive process to be one of 30 incoming Texas A\&M student participants.
        \item Traveled throughout Italy and attended lectures and tours on Italian art, architecture, and culture.
    \end{itemize}
}

\vspace*{-1\baselineskip}


%%%%%%%%%%
% HONORS %
%%%%%%%%%%

\section{Honors and Awards}

%\cvline{Pi Mu Epsilon (Math Honor Society)}{(2015-2016)---Elected Webmaster}
\cvline{National Merit Scholar}{(2014 - 2018)}
\cvline{Texas A\&M President's Endowed Scholar}{(2014 - 2018)}
\cvline{HackDFW}{(2016) Won Ilumi SmartBulb prize by developing Android app which provided light therapy for different medical conditions by automatically controlling light color and intensity.}
%\cvline{Math Fest}{(2015) Selected by honors faculty to attend national math conference.}
%\cvline{Capital One Summit for Developing  Leaders}{(2015) }

\end{document}